Viscous Erosion in Porous Media

### 2018-01-31 docs/methods/erosion_methods.tex
NM

We aim to measure the opening angle in our simulation, but, curiously, the body vanishes before a steady-state is definitively reached. To obtain the true terminal shape, we could restart our simulation with the final eroded body scaled up and iterate this process until reaching steady state. A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
\begin{equation}
\Vn \leftarrow \Vn - \mean{\Vn}
\end{equation}
This modification allows erosion to modify the body shape as it would normally, but artificially keeps the area of the body fixed. We show in Fig.~\ref{fixed_intface}a several interfaces at equally spaced times. Notice the body obtains the slender, football shape seen previously, but here more precision is available. We also show in Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes much more evenly distributed as time proceeds. In this figure, time is normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation shown in Fig.~\ref{shrink_intface}. Curiously, about 3 multiples of $t_f$ are required to reach a visually satisfying stead-state. This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which a reasonable steady-state was reached before the body vanished.

\todo{Cite previous erosion papers}

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}[p]%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
\caption{Aspect ratio and opening angle}
\label{fig:arangle}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}[p]%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
\label{table:arangle}
\begin{tabular}{c c c}
\hline
\hspace{0.5pc} smoothing parameters: $\eps$ and $\sigma$
\hspace{0.5pc} & final aspect ratio 
\hspace{0.5pc} & final opening angle \\
\hline
20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% npts = 1024

>>>>

We aim to measure the opening angle in our simulation, but, curiously, the body vanishes before a steady-state is definitively reached. To obtain the true terminal shape, we could restart our simulation with the final eroded body scaled up and iterate this process until reaching steady state. A simpler solution, though, is to remove the effect of shrinking during the erosion process by simply modifying the normal velocity $\Vn$ to have zero mean
\begin{equation}
\Vn \leftarrow \Vn - \mean{\Vn}
\end{equation}
This modification allows erosion to modify the body shape as it would normally, but artificially keeps the area of the body fixed. We show in Fig.~\ref{fixed_intface}a several interfaces at equally spaced times. Notice the body obtains the slender, football shape seen previously, but here more precision is available. We also show in Fig.~\ref{fixed_intface}b the stress, showing that the stress becomes much more evenly distributed as time proceeds. In this figure, time is normalized by the same vanishing time $t_f = 1.79E-2$ as the simulation shown in Fig.~\ref{shrink_intface}. Curiously, about 3 multiples of $t_f$ are required to reach a visually satisfying stead-state. This is very much in contrast to previous studies of erosion in high-Reynold's number flows, in which a reasonable steady-state was reached before the body vanished \cite{moo-ris-chi-zha-she2013}.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/arangle.pdf}
\caption{Aspect ratio and opening angle}
\label{fig:arangle}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
\label{table:arangle}
\begin{tabular}{c c c}
\hline
\hspace{0.5pc} smoothing parameters: $\eps$ and $\sigma$
\hspace{0.5pc} & final aspect ratio 
\hspace{0.5pc} & final opening angle \\
\hline
20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% npts = 1024
